Morbidity and transmission factors associated with variant B1.1.7

### 2021-02-10 beamerkable.Rmd
updated shielding markdown script before circulation

---
title: "beamer kable" 
author: PM 
output: 
  beamer_presentation:
    slide_level: 1
    includes:
      in_header: /mnt/phs/beamer_header.tex
    keep_tex: yes
---

# Title slide

# Table with kable

@@

knitr::kable(mtcars[1:4, 1:4], 
             escape=FALSE,
             booktabs=TRUE,
	label="regressionseverecasesnocare",
	caption="Rate ratios for severe COVID-19 in those not resident in care homes" 
	) %>% 
    add_header_above(c(" "=2, "Univariate"=2))

```
# more stuff

           format="latex", 
             escape=FALSE,
             booktabs=TRUE,
             label="regressionseverecasesnocare",
             caption="Rate ratios for severe COVID-19 in those not resident in care homes. ", 
             col.names=c(clean.header(colnames(table.shielded.severecases.nocare)[1:2]),
 #                        "Rate ratio (95\\% CI)", "\\ensuremath{p}-value",
                         "Rate ratio (95\\% CI)", "\\ensuremath{p}-value")) %>%
#    add_header_above(c(" "=3, "Univariate"=2, "Adjusted"=2)) %>%
    column_spec(column=1, width="3cm") %>%
    column_spec(column=2, width="2cm") %>%
    column_spec(column=3, width="2cm") %>%
#    column_spec(column=4, width="2.5cm") %>%
#    column_spec(column=5, width="2cm") %>%
#    column_spec(column=6, width="2.5cm") %>%
#    column_spec(column=7, width="2cm") %>%
    kableExtra::group_rows("Shielding eligibility category", 3, 8) %>%
#    kableExtra::group_rows("School-age children in household", 10, 12) %>%
#    kableExtra::group_rows("Adults in household", 13, 16) %>%
#    kableExtra::group_rows("SIMD quintile", 18, 22) %>%
#    kableExtra::group_rows("Occupation", 23, 26) %>%
    kable_styling(latex_options=c("scale_down", "HOLD_position")) %>%
    add_footnote(label=c("Percentages are column percentages for each variable",
                         "PF, patient-facing"), notation="none")

>>>>

---
title: "Morbidity and transmission factors associated with variant B1.1.7" 
author: "Paul McKeigue and Helen Colhoun" 
output: 
  beamer_presentation:
    slide_level: 1
    includes:
      in_header: ../beamer_header.tex
    keep_tex: yes
---

# 28-day fatality by S gene dropout status
\scriptsize
\setbeamertemplate{caption}{\raggedright\insertcaption\par}

@@

knitr::kable(table.death.coxph[3:5, c(1:2, 5:6)],
             escape=FALSE, 
             booktabs=TRUE,
			 label="coxfatal",
             row.names=TRUE,
             align=c("r", "r", "r", "l"), 
             col.names=c(clean.header(colnames(table.death.coxph)[1:2]),
                        "Rate ratio (95\\% CI)", "\\ensuremath{p}-value"), 
             caption="Death within 28 days of testing positive: Cox regression on S gene dropout and covariates") %>%
    column_spec(column=1, width="2cm") %>%
    column_spec(column=2, width="2cm") %>%
    column_spec(column=3, width="1.8cm") %>%
    column_spec(column=4, width="2.2cm") %>%
    column_spec(column=5, width="1.5cm") %>%
    add_footnote(label=c("Adjusted for age and sex",
                         "Stratified by days since testing positive and calendar week"),
                 notation="none")

```
# Test-positive cases: severity and cycle threshold

```{r plotvariantbydate, echo=FALSE, warning=FALSE, message=FALSE, fig.pos = "H", fig.asp=0.8}

theme_set(theme_gray(base_size = 18))

gA <- ggplotGrob(p.variantbydate)
gB <- ggplotGrob(p.mediansbydate)
grid::grid.newpage()
grid::grid.draw(rbind(gA, gB))

```

# Severe cases by source

```{r plotvariantbysource, echo=FALSE, warning=FALSE, message=FALSE, fig.pos = "H", fig.asp=0.75}

theme_set(theme_gray(base_size = 18))
p.bysource

```
